Lattices of acyclic pipe dreams

### 2023-12-22 acyclicFacets/draft/latticePipeDreams.tex
add reference to FPSAC
change affiliation

\author[V.~Pilaud]{Vincent Pilaud}
\address[V.~Pilaud]{CNRS \& LIX, \'Ecole Polytechnique, Palaiseau}
\email{vincent.pilaud@lix.polytechnique.fr}
\urladdr{http://www.lix.polytechnique.fr/~pilaud/}

\thanks{
NB was supported by NSERC and York Research Chair in Applied Algebra.
CC was supported by the Austrian Science Fund FWF (Project P 33278).
NC \& VP were partially supported by the French project CHARMS (ANR~19\,CE40\,0017).
CC, NC \& VP were also supported by the Austrian\,--\,French project PAGCAP (ANR~21\,CE48\,0020 \& FWF I 5788).
}

@@

\vspace*{-1cm}

@@

\vspace*{-.5cm}

>>>>

\author[V.~Pilaud]{Vincent Pilaud}
\address[V.~Pilaud]{Universitat de Barcelona}
\email{vincent.pilaud@ub.edu}
\urladdr{https://www.ub.edu/comb/vincentpilaud/}

\thanks{
NB was supported by NSERC and York Research Chair in Applied Algebra.
CC was supported by the Austrian Science Fund FWF (Project P 33278).
NC \& VP were partially supported by the French project CHARMS (ANR~19\,CE40\,0017).
CC, NC \& VP were also supported by the Austrian\,--\,French project PAGCAP (ANR~21\,CE48\,0020 \& FWF I 5788).
VP was a CNRS researcher at \'Ecole Polytechnique when this work was done.
\\
\hspace*{.5cm} 
Part of the material of this paper was announced in an extended abstract of the conference FPSAC'23~\cite{Cartier-FPSAC}.
}

@@

\vspace*{-1.2cm}

@@

\vspace*{-.7cm}
